\documentclass[a4paper]{article}
\usepackage[left=15mm,top=10mm,right=15mm,bottom=10mm]{geometry}
\usepackage{wrapfig}
\usepackage{array}
\usepackage{titlesec}
\usepackage{hyperref}
\pagenumbering{gobble}
\titlespacing*{\section}{0mm}{1.75mm}{0mm}
\author{Justin Soon}
\begin{document}
\section*{\huge\textbf Justin Soon}
\begin{minipage}{.45\linewidth}
	\begin{flushleft}
		B.S. Comp Sci, JMU\\
		Github id: \href{https://github.com/justinsoon}{justinsoon}\\
	\end{flushleft}
\end{minipage}
\hfill
\begin{minipage}{.45\linewidth}
	\begin{flushright}
		Email: \href{mailto:justin.soon@verizon.net}{justin.soon@verizon.net}\\
		Website: \href{http://justinsoon.github.io/}{justinsoon.github.io}\\
	\end{flushright}
\end{minipage}

%----Programming Projects and Open Source Contributions---%
\section*{Programming Projects and Open Source Contributions}
\hrule
\vspace{3mm}
\begin{itemize}
	\item
	      \textbf{In-toto, software security framework}
	      \hfill \textit{under Prof. Justin Cappos, May-July 2017}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
		\item Secures the integrity of software supply chain by GPG signing each step of software development.
		\item Worked on integrating in-toto in OpenSUSE linux to increase security of packages.
		\item Contributed new features, tests to the framework and fixed bugs. Increased code coverage.
		\item Full specifications and details at \href{https://in-toto.io}{in-toto.io}
	      \end{itemize}
	\item
	      \textbf{Autonomous Underwater Vehicle, robotics project}
	      \hfill \textit{under Prof. K.S. Venkatesh, 2014-2017}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
		\item \textbf{Software Team Head}, lead a team of 5 students since August 2015.
		\item Achieved \textbf{2nd place} at national level competition NIOT-SAVe in our debut attempt. (December 2016)
		\item Using OpenCV for Vision and Gazebo for simulator tests. Built using Robot Operating System.
		\item Set up Travis CI for automating building and deploying Doxygen docs to github gh-pages.
		\item Full design report at \href{http://auviitk.com}{auviitk.com}
	      \end{itemize}
	\item
	      \textbf{KeyboardNinja ruby on rails game}
	      \hfill \textit{October 2016}
	      \begin{itemize}
		\vspace{-2mm} \setlength\itemsep{-0.7mm}
		\item Online multiplayer typing game. The game is live at \href{https://keyboardninja.herokuapp.com}{keyboardninja.herokuapp.com}
		\item Developed RESTful APIs for creating, joining games and getting result.
		\item Built using Rails, Coffeescript, Postgres and deployed on Heroku.
	      \end{itemize}
	\item
	      \textbf{Antaragni Festival App}
	      \hfill \textit{May-October 2015}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
	      	\item Built the Android application for the golden jubilee of Antaragni, cultural festival of IIT Kanpur.
	      	\item Users can view schedule, event details, venue map and contact details of event organizer.
	      	\item Notifications, result declaration, reminders are provided through FCM.
	      \end{itemize}
	\item
	      \textbf{Android C IDE App}
	      \hfill \textit{under Prof. Amey Karkare, January-April 2015}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
	      	\item Users could write and run interactive C language programs, include standard library.
	      	\item Cross compiled tiny c compiler and libraries for different android architectures.
	      \end{itemize}
		\item
	      \textbf{Startup Weekend}
	      \hfill \textit{March 2015}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
	      	\item Secured 3rd place for developing a prototype app which helps find people to play sports with.
	      	\item After choosing a sport, users could view players on map and chat with all online players.
	      \end{itemize}
	\item
	      \textbf{Notable Open Source contributions}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
	      	\item Designed 2 customizable website \& blog templates for Jekyll. Released under MIT license.
	      	\item html-textview, added support for external image downloading libraries.
	      	\item Materialistic Hacker News, added option to reload saved page if offline data is cleared.
	      \end{itemize}
\end{itemize}

%--------Technical Skills--------%
\section*{Technical Skills}
\hrule
\vspace{3mm}
\begin{tabular}{@{}m{40mm}m{130mm}@{}}
	\textbf{\textrm{Languages}}        & Kotlin, Java, C/C++, Python, Bash, JavaScript, HTML5, CSS\\
	\textbf{\textrm{Frameworks/Tools}} & Android SDK, AngularJS, Rails, ROS, OpenCV, Bootstrap, Jekyll, Jenkins, Docker\\
\end{tabular}

%----Positions of Responsibility---%
\section*{Positions of Responsibility}
\hrule
\vspace{3mm}
\begin{itemize}
	\item
	      \textbf{Google Developer Group} Lead Coordinator
	      \hfill \textit{2015-2016}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
		\item Taught more than 15 sessions on Android, including tutorials for Software Architecture (CS654).
		\item Guided about 80 people through Google Study Jam and CS for Android online courses.
	      \end{itemize}
	\item
	      \textbf{Student Guide}
	      \hfill \textit{2015-2016}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
		\item Helped 7 new students while they familiarize with the rigours of college life.
	      \end{itemize}
	\item
	      \textbf{Mentoring Projects}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.7mm}
	      	\item Facilitated 3 students in various robotics club projects and 6 students in programming club project.
	      	\item Member of Navya, FLOSS group. Mentored 5 students in contributing to open source.
	      \end{itemize}
\end{itemize}

%----Extracurricular activities----%
\section*{Extracurricular activities}
\hrule
\vspace{3mm}
\begin{itemize}
	\setlength\itemsep{-0.7mm}
	\item Secured 1st place in intra-college tournament Josh chess 2015. Part of college chess team 2014.
	\item All India Rating Chess Tournament 2012, secured 56th place amongst 200 participants.
	\item Secured 2nd position in Basketball in Fresher’s Inferno in 2014, intra-college sports event.
	\item Secured 2nd position in Lucknow Zonal BasketBall Championship 2013.
\end{itemize}

\end{document}
